### 2021-07-04 docs/manuscript/manuscript.tex
Rephrase Abstract::Results

\subsection*{Results}
Out of 2061 GRNs selected using the genetic algorithm, we found 714 groups of
topologies that were able to interpret a morphogen input. The main network motif
involved in the formation of the band expression pattern was the type 3
Incoherent Feed Forward Loop (I3-FFL); we also present here other network
topologies that have not been previously reported and that can be useful as
synthetic regulatory networks due to its simple design and robust morphogen
interpretation mechanisms.

>>>>

\subsection*{Results}
Out of 2061 GRNs selected using the genetic algorithm, we found 714 groups of
network topologies that were able to correctly interpret the morphogen.
Importantly, the main network motif found to generate the target phenotype in
response to the input signal was the type 3 Incoherent Feed Forward Loop (I3-FFL),
which is in agreement with previous theoretical expectations and experimental
observations. Notably, compared to previously reported pattern forming GRN
topologies, we have uncovered a great variety of novel network designs, some of
which might be worth inquiring through synthetic biology methodologies to test
for the ability of network design with minimal regulatory complexity to robustly
interpret a developmental cue.
